---
title: "lab07"
author: "Dylan Scoble"
date: "3/4/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(broom)
library(pROC)
library(plotROC)
library(knitr)
```


```{r}
spotify <- read_csv("spotify.csv")
glimpse(spotify)
```

# Part 1: Data Prep & Modeling


### Exercise 1
```{r}
spotify <- spotify %>% 
  drop_na() %>% 
  mutate(target = as.factor(target),
         key = case_when(
           key == 2 ~ "D",
           key == 3 ~ "D#",
           TRUE ~ "Other"
         ))

glimpse(spotify)
```

```{r}
ggplot(data = spotify, aes(x = key, fill = target)) +
  geom_bar(position = "fill") +
  labs(title="Target vs Key",
       y="Proportion")
```
The plot above describes the relationship between Key and Target. For all songs in the key of D, about 60% of them have a target value of 1. For all songs in the key of D#, about 30% of them have a target value of 1. For all other songs, about half of them have a target value of 1.

### Exercise 2

```{r}
model <- glm(target ~ acousticness + danceability + duration_ms + instrumentalness + loudness + speechiness + valence, data = spotify, family = binomial)

tidy(model, conf.int = TRUE, exponentiate = FALSE) %>%
  kable(format="markdown", digits = 5)
```

### Exercise 3

```{r}
model_with_key <- glm(target ~ acousticness + danceability + duration_ms + instrumentalness + loudness + speechiness + valence + key, data = spotify, family = binomial)

summary(model)$aic

summary(model_with_key)$aic

```

Adding key to the model lowers the model's AIC, making it better at predicting target. Therefore, we will continue to use the model with key.

### Exercise 4

```{r}
tidy(model_with_key, conf.int = TRUE, exponentiate = FALSE) %>%
  kable(format="markdown", digits = 5)

```

If the key of the observation is D#, the target value's prediction will increase, by a value of exp(-1.07319).

# Part 2: Checking Assumptions

### Exercise 5

```{r}
df <- augment(model_with_key, type.predict = "response",type.residuals = "deviance")
glimpse(df)
```

### Exercise 6

```{r}
arm::binnedplot(x = df$.fitted, y = df$.resid,
                xlab = "Predicted Probabilities", 
                ylab = "Residuals",
                main = "Binned Residual vs. Predicted Values", 
                col.int = FALSE)
```

### Exercise 7

```{r}
arm::binnedplot(x = df$danceability, y = df$.resid,
                xlab = "Danceability", 
                ylab = "Residuals",
                main = "Binned Residual vs. Danceability", 
                col.int = FALSE)
```

### Exercise 8

```{r}
df %>% 
  mutate(key_resid = if_else(.resid > 1 | .resid < -1, "High Residual", "Low Residual")) %>% 
  group_by(key, key_resid) %>% 
  summarise(n = n()) %>%
  kable(format="markdown")
```

### Exercise 9

The linearity assumption is not satisfied because there is no clear linear relationship between our fitted values and our predictors, as shown by the plot in exercise 6.



